### 2020-12-20 paper/introduction.tex
Enforced 88 character limit.

\begin{enumerate}
    \item At the core of the model, people meet people based on a matching algorithm. We distinguish various types of contacts. Currently, these are households, leisure activities, schools, nurseries and several types of contacts at the workplace. Contact types can be random or recurrent and vary in frequency.
    \item Policies can be implemented as shutting down contact types entirely or partially. The reduction of contacts can be random or systematic, e.g., to allow for essential workers.
    \item Infection probabilities vary across contact types, but are invariant to policies which reduce contacts.
    \item The model achieves a good fit on German infection and fatality rate data even if only the infection probabilities are fit to the data and the remaining parameters are calibrated from the medical literature and datasets on contact frequencies.
    \item High quality Python code for the model is freely available on Github, well documented and very flexible\footnotemark. We are actively looking for researchers who want to use our model for their projects.
\end{enumerate}

\footnotetext{The code can be found under \url{https://github.com/covid-19-impact-lab/sid} and the documentation with tutorials and background information under \url{https://sid-dev.readthedocs.io/}.}

>>>>

\begin{enumerate}
    \item At the core of the model, people meet people based on a matching algorithm. We
          distinguish various types of contacts. Currently, these are households,
          leisure activities, schools, nurseries and several types of contacts at the
          workplace. Contact types can be random or recurrent and vary in frequency.

    \item Policies can be implemented as shutting down contact types entirely or
          partially. The reduction of contacts can be random or systematic, e.g., to
          allow for essential workers.

    \item Infection probabilities vary across contact types, but are invariant to
          policies which reduce contacts.

    \item The model achieves a good fit on German infection and fatality rate data even
          if only the infection probabilities are fit to the data and the remaining
          parameters are calibrated from the medical literature and datasets on contact
          frequencies.

    \item High quality Python code for the model is freely available on Github, well
          documented and very flexible\footnotemark. We are actively looking for
          researchers who want to use our model for their projects.
\end{enumerate}

\footnotetext{
    The code can be found under \url{https://github.com/covid-19-impact-lab/sid} and the
    documentation with tutorials and background information under
    \url{https://sid-dev.readthedocs.io/}.
}

### 2020-12-20 paper/medical_parameters.tex
Enforced 88 character limit.

    \tablenotes{The data is taken from \citet{Stokes2020} and \href{https://github.com/BDI-pathogens/OpenABM-Covid19/blob/572e24ca2dbf7153789a92ad3a27e4c515d0e576/documentation/parameters/parameter_dictionary.md}{the OpenABM-Project}.}

>>>>

    \tablenotes{
        The data is taken from \citet{Stokes2020} and
        \href{https://github.com/BDI-pathogens/OpenABM-Covid19/blob/572e24ca2dbf7153789a92ad3a27e4c515d0e576/documentation/parameters/parameter_dictionary.md}{the
        OpenABM-Project}. }
